Online Verification of Commutativity

### 2020-08-11 acmPaper/paper.tex
Finish problem pass

The \textsc{Online addition problem}, given a commuting diagram and a new edge, returns whether the diagram commutes.
Checking function equality is a domain specific, potentially hard problem, dependent on the nature of the graph.
For our case study in graphics programming (see Section~\ref{sec:gator}), edges are matrices and nodes are vector spaces, so function composition uses matrix multiplication and equivalence checking simply compares matrix values.
We therefore assume some oracle for checking transformation function equivalence that will vary by domain.
%
We therefore reduce the \textsc{Online addition problem} to the \textsc{Verification set problem}.
The latter, when given a diagram and a new edge, returns the set of parallel pairs of paths, such that if and only if the members in each pair are equal, then the new graph must commute.
The output to the \textsc{Online addition problem} can then be obtained as whether equality checking for all pairs succeeds.

The oracle would needs to preserve that equality is reflexive, symmetric and transitive in order to benefit from the guarantees of the algorithms below.
For example, the oracle for currency graph (Section ~\ref{sec:currency}) only approximately preserves transitivity because of floating point error magnification, so while the algorithm catches mistakes, it does not guarantee that the diagram commutes.

>>>>

The \textsc{Online addition problem}, given a commuting diagram and a new edge, returns whether the diagram commutes.
Checking function equality is a domain specific, potentially hard problem, dependent on the nature of the graph.
For our case study in graphics programming (see Section~\ref{sec:gator}), edges are matrices and nodes are vector spaces, so function composition uses matrix multiplication and equivalence checking simply compares matrix values.
We therefore assume some oracle for checking transformation function equivalence that will vary by domain.
%
We therefore reduce the \textsc{Online addition problem} to the \textsc{Verification set problem}.
\xxx[as]{Although it's not technically a ``reduction,'' is it? Maybe better to say that the latter is what we solve, and we assume an oracle that uses those results to solve the former.}
The latter, when given a diagram and a new edge, returns the set of parallel pairs of paths, such that if and only if the members in each pair are equal, then the new graph must commute.
\xxx[as]{Let's be precise around the ``equal'' terminology in the previous and next sentences. It's not that the pairs are equal---it's that we check function equivalence for the pairs' corresponding functions.}
The output to the \textsc{Online addition problem} can then be obtained as whether equality checking for all pairs succeeds.

The algorithms in the rest of the paper assume that the function equivalence oracle is reflexive, symmetric, and transitive.
\xxx[as]{The following is a little tricky to understand here... maybe this is best left to the currency section?}
For example, the oracle for currency graph (Section~\ref{sec:currency}) only approximately preserves transitivity because of floating point error magnification, so while the algorithm catches mistakes, it does not guarantee that the diagram commutes.
